---
title: "HDAT9800 Chapter 1"
description: |
  Chapter 1 material for HDAT9800 Visualisation & Communication of Health Data
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(fontawesome)
library(knitr)
library(kableExtra)
library(dplyr)
library(hexSticker)
library(ggplot2)
library(shiny)
library(vembedr)

options(kableExtra.html.bsTable = T)

```

# Pre-recorded lectures for Chapter 1

## Course overview including course aims and principles (Chapter 1 - Course Overview - Part 1)

```{r ch1-part1-video, preview=TRUE}
embed_url("https://youtu.be/Zqfj-kredzs")
```

## Introduction of chapter topics including R, dplyr, literate programming, git, ggplot2, collaborating with git, leaflet, shiny and the shiny group project (Chapter 1 - Course Overview - Part 2)

```{r ch1-part2-video, preview=TRUE}
embed_url("https://youtu.be/CCR5-RylUoY")
```

## Slide deck for Course Overview

[Slide deck for Chapter 1 - Course Overview - Part 1 & 2](assets/HDAT9800-2022-T2-Chapter-1.pdf)


## Using git for version control (Chapter 1 - Version control with git and GitHub - Part 1)

```{r ch1-git-part1-video, preview=TRUE}
embed_url("https://youtu.be/RSmu0P4jUgI")
```

## Setting up and configuring git, setting up git with RStudio, how to access the assessment repository and the chapter 1 assessment (Chapter 1 - Version control with git and GitHub - Part 2)

```{r ch1-git-part2-video, preview=TRUE}
embed_url("https://youtu.be/2rMQZDm2gXE")
```

## Slide deck for git and GitHub lecture

[Slide deck for Chapter 1 - git and GitHub  - Part 1 & 2](assets/HDAT9800-Chapter-1-git.pdf)


View the lecture videos, and download the lecture notes if you want to follow along with the presenter (or for revision later). 

After you have viewed the lectures, please proceed to do the tutorials.

# Tutorials for Chapter 1

Please follow the instructions for installing the `cbdrhintro` tutorials package for R on the [course home page](index.html) and proceed to do the `dplyr` tutorial.

If you are unfamiliar with R, you should also work through the six introduction to R tutorials that are also conained in and installed by that package.




```{r, eval=FALSE, incude=FALSE}

## Week 1. Directed Acyclic Graphs (DAGs)
# ```{r}

reading = c(
      "Miguel A. Hernán, John Hsu & Brian Healy (2019) A Second Chance to Get Causal Inference Right: A Classification of Data Science Tasks, Chance, 32(1), 42-49",
      "Austin, Anna E., Tania A. Desrosiers, and Meghan E. Shanahan. Directed Acyclic Graphs: An under-utilized tool for child maltreatment research. Child Abuse & Neglect 91 (2019): 78-87",
      "Shmueli, Galit. To Explain or to Predict? Statist. Sci. 25 (2010), no. 3, 289-310",
      "The importance of being clear about your question & using that to drive your methods, a tweetorial by epidemiologist Dr Ellie Murray from Boston University School of Public Health.",
      "dagitty.net A great website explaining DAGs and related topics, with built-in applets to test your knowledge",
      "An excellent YouTube video series on Causality and DAGs presented by Assistant Professor Nick Huntington-Klein from Seattle University. This is a series of 14 videos that starts from the very basics of causal thinking with DAGs"
    )

links <- c(
  "<a class='fa fa-file-pdf' href='https://www.tandfonline.com/doi/full/10.1080/09332480.2019.1579578' target='_blank'></a>",
  "<a class='fa fa-file-pdf' href='https://doi.org/10.1016/j.chiabu.2019.02.011' target='_blank'></a>",
  "<a class='fa fa-file-pdf' href='https://www.galitshmueli.com/system/files/Stat%20Science%20published.pdf' target='_blank'></a> <a class='fab fa-youtube' href='https://www.youtube.com/watch?v=vWH_HNfQVRI&t=1s' target='_blank'></a>",
  "<a class='fa fa-twitter' fill = 'lightblue' href='https://twitter.com/EpiEllie/status/1214641734900224003' target='_blank'></a>",
  "<a class='fa fa-laptop' href='dagitty.net' target='_blank'></a>",
  "<a class='fab fa-youtube' href='https://www.youtube.com/playlist?list=PLcTBLulJV_AKmUTH-nUsxxFyRQoWnUzxU' target='_blank'></a>"
)


df <- data.frame(
  reading = reading,
  links = links
)


kbl(df, escape = FALSE,
    align = c('l', 'c'),
    col.names = NULL) %>%
  kable_styling(bootstrap_options = "hover") %>% 
    kableExtra::group_rows(start_row = 1, end_row = 2, group_label = "Core readings") %>% 
    kableExtra::group_rows(start_row = 3, end_row = 6, group_label = "Other resources") 

# ```

<aside>

<br>

You should prioritise the core readings each week.  

Note that some of the links below will require you to be logged in to your UNSW library account to access. 

</aside>
'''





