---
title: "Recordings"
description: "Explanatory videos"
---

# Week 1. Directed Acyclic Graphs (DAGs)


```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://www.youtube.com/embed/lhkmc-dXC7M", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),       
 
tags$div(class = "boxVid", tags$iframe(src="https://www.youtube.com/embed//DhHBMvpYeec", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Representing common causal structures with DAGs")),  

tags$div(class = "boxVid", tags$iframe(src="https://www.youtube.com/embed/6X8yc9qY96M", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Identifying frontdoor and backdoor paths")),

tags$div(class = "boxVid", tags$iframe(src="https://www.youtube.com/embed/gIeQymUfyBM", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Closing pathways to estimate causal effects")),
         
)

```

<aside>

<br>

To watch the video in full-screen, first click play then choose Full screen. 

</aside>

# Week 2. Matching for causal inference from observational data

```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/cvb17LGNKQ4", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),     

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/rgXD4MnPDgc", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Identifiability assumptions")),   

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/bOA954e4HcU", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Exact matching and coarsened exact matching")),   

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/q2RE86gZ2Yg", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Distance-based matching")),   

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/ABqX6h6I9d4", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Mahalanobis distance")),   

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/8dRpXafdcF4", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Propensity score distance")),
         
)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>

# Week 3. Multilevel modelling I (Introduction)

```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/OzGgbrGn7ls", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/eBItxNkZCLs", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Introducing multilevel data and multilevel models")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/mEcXhYNkJ38", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Fixed parameters or random variables")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/v5QKE7HoGuc", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Residuals and partitioning the variance")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/BIroLtHSKGk", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Correlated random effects")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/Yd0lH6O_X4I", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Multilevel models in R")), 
         
)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>


# Week 4. Multilevel Modelling II (Beyond the basics)

```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/8SnPFQK0hf0", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/-Pdzm-1E75E", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Model building and comparison")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/QrZ9U9tpb7E", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Model predictions")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/U3inYIjaBNo", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Modelling binary outcomes")), 
         
)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>


# Week 7. Time Series Analysis

```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/W6Vfa3wEfjU", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/eMp3s_X2uOc", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("What are time series data?")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/YZ9LrP5O9wc", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Visualising time series data")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/UEWbiPB81Fk", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Characterisitcs of time series data")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/9wQJTOOS6lQ", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Statistical properties of time series data")), 

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/DlHmaTqvCxQ", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("ARIMA models"))
         
)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>


# Week 8. Interrupted Time Series Analysis

```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/hEKYDvGzOFw", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/4o_DDdhPz7Y", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("What is interrupted time series analysis?")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/vbZU8tq-IUw", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Segmented regression")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/soL_RXNAIqE", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Model choice"))
         
)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>


# Week 9. Missing Data and Multiple Imputation

```{r, echo = FALSE}
tags$div(class = "boxChapter",

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/VSEqd6MuKP0", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Iterative Chained Equations (ICE)")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/H1kAcipjUH4", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Advantages of the ICE algorithm")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/XGy-OYqvC-0", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("How the ICE algorithm works")),  

tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/QxLMUv7YKU0", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("How many cycles for ICE?"))
         
)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>


# Week 10. Presenting and summarising model results

```{r, echo = FALSE}
tags$div(class = "boxChapter",
         
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/T4X8i4H_Rpo", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Overview")),  
   
tags$div(class = "boxVid", tags$iframe(src="https://youtube.com/embed/gbokhfMdfE8", title="YouTube video player", frameborder="0", allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; fullscreen")),        
tags$div(class = "boxText", tags$p("Interpreting and Presenting Statistical Results by Professor Gary King")),        


)

```

<aside>

<br>

[Back to the top `r fontawesome::fa("arrow-up")`](recordings.html) 

</aside>
